\section{Related work}
In last few years, crowd-sourcing data from social media 
as a large scale and free to public data source
has 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{received lots of attention from; or 
%(become more and more popular to)} 
researchers working on using textual contents to
predict elections~\cite{you2015multifacetedelections},
using geo-tags to quantify
tourism in nature area using geo-tag profile of social media users ~\cite{wood2013usingtourism},
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{talk a lot about motivation of scientific report paper since it's in nature area}
%to draw coastline~\cite{omori2014can},
%~\cite{Can geo-tags on flickr draw coastlines?}, 
using geo and temporal tags to analyze people's event-based activity 
when large group of people gathering together during a function of time 
such as football match,
and using both geo and textual tags to 
extract land use information from Panoramio~\cite{vsecerov2015analysis, oba2014towards}, 
%~\cite{Analysis of panoramio photo tags in order to extract land use information, Towards Better Land Cover Classification Using Geo-tagged Photographs},
in~\cite{ecology2012www}, 
Zhang \etal estimates snowfall and vegetation coverage 
based on geo, temporal and textual tags of Flickr images. 
%\fxnote{accuracy of geo-temporal problem, and now it's getting better.}

Since public-sharing photos provides such a huge potential in social and environmental study, it's 
natural to see a lot of works start analyzing image contents. Webcam providing dense temporal images 
is a good source to monitor the nature. A series of works explore sequences 
of webcam images describing outdoor scene with 40 transient attributes~\cite{laffont2014transient}, estimating dynamic cloud maps ~\cite{murdock2015building, murdock}, exploring interactions between visual elements and the temperature 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{or just as the title: exploring correlations between appearance and temperature} ~\cite{glasner2015hot}, 
and monitoring the dynamic snow phenomena at mountain areas ~\cite{fedorov2015snowwatch, fedorov2014snow}. 
To evaluate the study of temperature, cloud, and snowfall amount,
 researchers can easily compare their results with satellite maps. 
Some works also use crowd-sourcing data from other sources, for example, Google street view provides selectively dense geo distributed images to help navigating the environment ~\cite{khosla2014looking} and understanding urban scene and predicting urban perception ~\cite{porzi2015predicting}, and Li \etal use the co-occurrence statistics of celebrities appears on news images to auto tag photographs of celebrity community ~\cite{li2015celebritynet}
%\fxnote{give a term like social identity?}. 
Unfortunately, 
the evaluation in these works are either not in continental scale or just via quality visualization.
Performance of social activity studies, on the other hand, are even harder to evaluate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{say more about our evaluation? or move this to another place?}

Flickr and Panoramio as very popular photo-sharing websites 
``involuntarily'' support researchers identifying salient city attributes and analyzing the visual similarity among different cities in order to apply computer vision to urban planning ~\cite{zhou2014recognizing}
Photo-sharing websites collecting visual contents directly from people's activity and their surrounding areas which is so important, hard to collect otherwise but also very noisy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{write something about so there are very few work appears and so we are working on this?}

%\fxnote{not sure about keeping this paragraph or not. it seems duplicate of the 2 paragraphs above}

The fact that webcam can only be placed far away from people 
 makes it almost impossible to monitor people's activity, even not the surrounding area close to
residential or 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{crowd? I mean groups of people like downtown, not ski activity but like people 
%going to work and back everyday also a good topic to use temporal dense images but Webcam is not good 
%at this.}
 Social media, on the other hand, provides a larger freedom on location distribution. 
In fact, as a complementary, almost all the photos shared online are from locations people usually go to. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{how helpful is this to study more areas close to urban planning, market sharing, everyday living,
%anything related to people}

Our work take the advantage of studying ecology phenomena with 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\fxnote{easy to get, more reliable}
 satellite maps as
 ground truth and use social media data to \fxnote{monitor? insight?} these information from 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% \fxnote{locations more related to people}
 . We provide continental scale quantitative evaluation and introduce our
 method to tackle the problem of noisy and biased data, in order to support extended studies in other areas. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \fxnote{just want to say more areas in natural or not only natural but also social}

